---
title: "Lab 01 - Hello R"
author: "Fiona Wang"
date: "Jan-21-2025"
output: 
  html_document: 
    fig_height: 7
    highlight: kate
    theme: cerulean
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

Based on the help file, this data set has 1846 rows and 3 columns. The three variables included in the data frame are "dataset", "x", and "y". 

### Exercise 2

```{r plot-dino, fig.height=6, fig.width=9}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
After plotting the data from the dino data set, we got a dinosaur-shaped graph. Even though there didn't seem to be a linear relationship between x and y variables from observing the graph, a correlation analysis was conducted. There is a very weak and negative correlation  between x and y, r = -.0645.There is no p-value to determine whether it is significant or not. But since it's very weak, I would guess that it is not significant.

### Exercise 3

```{r plot-star, fig.height=4, fig.width=4}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The star dataset end up having a star-shaped graph after plotting x and y variables within in the dataset.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
From observing the graph, it didn't seem like a linear relationship. Correlation analysis showed that there is a weak and negative relationship between x and y for the star dataset, r = -.0630. This r value is quite close to the dino dataset. Again, there is no p value for significance testing, but given that it is very weak, I think it's not significant. Both dino and star dataset have very cool graphs, but neither has a linear relationship.

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point() +
  coord_fixed()
```

As we can see from the graph, the data points in the circle data set forms a circle-shaped graph. I also see three data points lying out of the circle.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```
From the correlation analysis, there is a weak and negative relationship between x and y in the circle dataset, r = -.0683. It's slightly more negative than the dino data set, but really they are quite similar. I would guess that this is also not a significant correlation. So far, all three datasets have shapes that correspond to their names. X and y variables had no linear relationship (or very weakly negative relationship) for all three datasets.

### Exercise 5

```{r plotting all data, fig.height=10, fig.width=10}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() + 
  facet_wrap (~dataset, ncol = 3) +
  theme(legend.position = "none")
```

It's really cool to see all these 13 datasets!! P.S. It's interesting that I cannot get the circle plot to look like a circle, it's more like an oval here.

```{r correlation for all dataset}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r=cor(x,y))
```

We can see that the correlations are all very close to each other, around -.065. This shows that x and y in all of the dataset are not correlated with each other, at least not linearly. 

This is the end of Lab01.  
